---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# fgitR

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![Codecov test coverage](https://codecov.io/gh/FastGitORG/fgitR/branch/main/graph/badge.svg)](https://codecov.io/gh/FastGitORG/fgitR?branch=main)
<!-- badges: end -->

[FastGit](https://doc.fastgit.org/) can work as a mirror of GitHub to make significant acceleration.

`fgitR` is a package to do git operation with FastGit automatically. 

For current stage, `fgitR` is only tested under macOS, and it should works well on OS with POSIX. For Windows, we will test and fix in the future.

## Installation

Once the initial development finish, we will post `fgitR` to CRAN.
So for, please install development version of `fgitR` from GitHub:
<!-- You can install the released version of fgitR from [CRAN](https://CRAN.R-project.org) with: -->

``` r
# For initial install
remotes::install_github("FastGitORG/fgitR")

# For upgrade installed `fgitR`
fgitR::fgit_install("FastGitORG/fgitR")
```

## Install package from Source

```{r install_package_from_source, cache=TRUE}
library(fgitR)

# fgitR can install package by Repository's Name
# fgitR_install("https://github.com/r-lib/diffviewer")

# fgitR can install package by Repository's URL
fgit_install("r-lib/diffviewer")
```

## List all branch from Remote

```{r list_branch, cache=TRUE}
branch_ls <-
  fgit_branch("https://github.com/tidyverse/tidyverse/")

head(branch_ls, n = 15)
```

## To-Do

- [X] Branch
- [ ] Head

### Questionary

For the initially consideration, we believe it is necessary to add following functions:

- Commit
- Pull
- Push

Due to `git` is not only clone to local, but also contribute back. But in the `git clone` or `fgit clone` procedure, the remote will be set as `fastgit.org` or other mirror domain. Hence, there is nothing special to make further operations.

There is definitely no reason to reinvent the wheel, import functions from `git2r` to implement `git clone`, `git pull` and `git push` should be fantastic. However, `git2r` is a GPL licensed project, while `fgitR` is under MIT. I am not sure if it is acceptable to import involving functions from `git2r` to `fgitR` without changing license? 

**P.S. I am not considering to change my license.**

## Bug report

It's very common for API upgrades to make the downstream application, like amapGeocode,which is unavailable. Feel free to [let me know](mailto://chenhan28@gmail.com) once it's broken or just open an <a class="github-button" href="https://github.com/FastGitORG/fgitR/issues" data-color-scheme="no-preference: light; light: light; dark: dark;" data-size="large" aria-label="Issue FastGitORG/fgitR on GitHub">Issue</a>.

## Code of Conduct

Please note that the fgitR project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
