---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# fgitR

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

[FastGit](https://doc.fastgit.org/) can work as a mirror of GitHub to make significant acceleration.

`fgitR` is a package to do git operation with FastGit automatically. 

For current stage, `fgitR` is only tested under macOS, and it should works well on OS with POSIX. For Windows, we will test and fix in the future.

## Installation

Once the initial development finish, we will post `fgitR` to CRAN.
So for, please install development version of `fgitR` from GitHub:
<!-- You can install the released version of fgitR from [CRAN](https://CRAN.R-project.org) with: -->

``` r
# For initial install
remotes::install_github("womeimingzi11/fgitR")

# For upgrade installed `fgitR`
fgitR::fgitR_install("womeimingzi11/fgitR")
```

<del>And Yes, in the future, there will be a function like `fgitR::install_fgit("womeimingzi11/fgitR")` to accelerate the installation of development version of `fgitR`.</del>

## Install package from Source

```{r install_package_from_source, cache=TRUE}
library(fgitR)

# fgitR can install package by Repository's URL
fgitR_install("r-lib/diffviewer")

# fgitR can install package by Repository's Name
fgitR_install("https://github.com/r-lib/diffviewer")
```

## To-Do

- [ ] Branch
- [ ] Head
- [ ] Commit (may be imported from git2r)
- [ ] Pull
- [ ] Push

## Code of Conduct

Please note that the fgitR project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
