---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# fgitR

<!-- badges: start -->
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)
[![Codecov test coverage](https://codecov.io/gh/FastGitORG/fgitR/branch/main/graph/badge.svg)](https://app.codecov.io/gh/FastGitORG/fgitR?branch=main)
<!-- badges: end -->

[`FastGit`](https://doc.fastgit.org/) works as a mirror of `GitHub` to make significant accelerations.

`fgitR` is a package to do git operation with `FastGit` automatically.

## Installation

`figtR` has been released in [CRAN](https://CRAN.R-project.org/package=fgitR). You can install the released version of fgitR from [CRAN](https://CRAN.R-project.org) with:

``` r
# Install from CRAN
install.packages("fgitR")

# Compiling from Source
remotes::install_github("FastGitORG/fgitR")

# For upgrade installed `fgitR`
fgitR::fgit_install("FastGitORG/fgitR")
```

## Install package from Source

```{r install_package_from_source, cache=TRUE}
library(fgitR)

# fgitR can install package by Repository's Name
# fgitR_install("https://github.com/r-lib/diffviewer")

# fgitR can install package by Repository's URL
fgit_install("r-lib/diffviewer")
```

## List all branch from Remote

```{r list_branch, cache=TRUE}
branch_ls <-
  fgit_branch("FastGitORG/fgitR")

branch_ls
```

### Reinventing the wheel?

For the initially consideration, we believe it is necessary to add following functions:

-   Commit
-   Pull
-   Push

Due to `git` is not only clone to local, but also contribute back. But in the `git clone` or `fgit clone` procedure, the remote will be set as `fastgit.org` or other mirror domain. Hence, there is nothing special to make further operations.

## Bug report

Feel free to [let me know](mailto://chenhan28@gmail.com) once it's broken or just open an <a class="github-button" href="https://github.com/FastGitORG/fgitR/issues" data-color-scheme="no-preference: light; light: light; dark: dark;" data-size="large" aria-label="Issue FastGitORG/fgitR on GitHub">Issue</a>.

## Code of Conduct

Please note that the fgitR project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
